\Character[Kushagra -- John Titor - A US Army soldier from the year 2236]{JOHN TITOR}{john}
\Character[Akash -- A renowned NASA scientist]{SCIENTIST (NASA)}{scone}
\Character[Vansh -- A renowned scientist from CERN]{SCIENTIST (CERN)}{sctwo}
\Character[Yuvraj -- A News24X7 news reporter]{REPORTER}{rep}

\DramPer

\scene[-- Debate Panel]

\StageDir{
    \begin{center}
        Sitting in a Debate panel, a video is shown to the viewers.
    \end{center}
}

\begin{drama}

    \repspeaks Hello and welcome to the fission TV news. My name is Yuvraj and I welcome you to prime time on science.
    Out topic today is about John Titor and his past videos from the 2000's that have surfaced as a shock fot the whole world.

    Let's take a look at one of John Titor's videos.

    \johnspeaks Hello folks of the 21st century,
    This is John Titor,
    A solider from the 32nd venture of the US time travel in the year 2236.
    This is my message to the past, the present, to you.

    The 7th world war was very devastating to the entire human race. I will be presenting to you the key events that led to the world war 3.

    \repspeaks \direct{Pauses Video} Here comes a clear warning of the future mishappening. Let's continue.

    \johnspeaks The year 2020, the pandemic which kick-started the century of nuclear wars.
    United Nations civil war which affected the elections of all the subsequent years.

    What ever you all are going the do, if world war III is not prevented, it will be the end, and it will be the end of it all, there will be no more do-overs.


    I know this will start riots and people will be disheartened, but it will have to be dealt with gracefully.


    To reverse the choice of the Stein's gate is our mission.

    \repspeaks Keeping the above objection in mind, now let's go live to Dr. Vansh in Switzerland and scientist Akash who is live from NASA.

    \sctwospeaks Good evening, everyone, this is Vansh, from CERN Switzerland. I am a nuclear researcher taking a stand for time travel.

    \sconespeaks Good evening, this is Akash from NASA, and I am taking a stand against time travel and I believe that John Titor’s videos are forged and fake.
    \sctwospeaks I believe that John Titor actually time travelled and came from the future. First and foremost, the argument I’ll throw is that he predicted key future events which have been instrumental in the course of the history of this planet. He predicted the unprecedented pandemic of 2020 that shook the whole world and also the dangerous Ukraine-Russia war that, he said, was the key point which led to World War 3 and has led to the destruction of the whole planet triggering multiple wars, one after the other.
    \sconespeaks I disagree with what you stated, Dr. Vansh. The predictions made by John Titor were really generic and a throw out in the void, made in a way they were going to be true one day. Something like a pandemic or a “war between two giant countries” is a very generic prediction that is inevitable. Bill Gates himself predicted a pandemic in 2015. Which is why I believe that he was a conman and just wanted attention.
    \repspeaks We would certainly not just talk about the conspiracy theories that surround John Titor, but we would also like to explore the philosophy behind what this whole fiasco stands on.
    \sconespeaks I am against the concept of time travel and there are valid reasons for my stand. One of the strongest arguments that has been put forth in the science community is the second law of thermodynamics. It states that the entropy of the universe is always, and hence, as a result, the universe gets more disordered as time passes. For time travel to happen, we need to have a reversible reaction, where the universe becomes more ordered, which is not possible.
    \sctwospeaks Dr. Akash I understand your point but completely relying on the present concepts of science may not be a good start. Our current understanding itself has so many flaws, and thus it becomes necessary for us to start thinking out of the box. The perfect example of this would be that in 1903, experts were clear that no flying machine could ever be built in the next 1-10 million years. And later that very same year, the Wright brothers flew at Kitty Hawk
    \repspeaks Dr. Akash and Dr. Vansh, could you give us a brief account of the philosophy surrounding time travel ?
    \sctwospeaks As John Titor says he is a time traveler, and I being a believer in the concept of it, I believe in Eternalism. The idea that the past and future exist in a real sense, not only as changes that occurred or will occur to the present.
    \sconespeaks And I am a believer of Presentism. It is a school of philosophy that holds that the future and the past exist only as changes that occurred or will occur to the present, and they have no real existence of their own. In this view, time travel is impossible because there is no future or past to travel to.
    \repspeaks Thank You, Akash and Vansh for your stand on this topic. I would like to apologize for interrupting since the time is up.
    \repspeaks We certainly couldn't arrive at a conclusion. Still Dr. Akash and Dr. Vansh helped us give a clear vision on the whole conspiracy that has been surrounding us regarding John Titor.
    We will be back tomorrow with another hour of exciting science discussion. Until then, this is Yuvraj Singh signing off.

\end{drama}
